QPLIB: A Library of Quadratic Programming Instances

### 2016-12-20 QPLIB-1.0.tex
updated application table

\framebox{TASK 2 : write motivation}

@@

On the other hand, (MI)QP is, in some sense, a considerably more expressive class than (MI)LP. Quadratic expressions are found, either naturally or after appropriate reformulations, in very many practical problems \cite{Kochenberger2014}. We survey several of these applications in Table \ref{tbl:application}. In general, any continuous function can be approximated with arbitrary accuracy (over a compact set) by a polynomial of arbitrary degree; in turn, every polynomial can be broken down to a system of quadratic expressions. Hence, (MI)QP is, in some sense, roughly as expressive as the whole of (MI)NLP. Of course this is, in principle, true for (MI)LP as well, but at the cost of much larger and much more complex formulations ({\bf citations?}). Hence, for many applications QP may represent the ``sweet spot'' between the effectiveness, but lower expressive power, of (MI)LP and the higher expressive power, but much higher computational cost, of (MI)NLP.

@@

Problem & Discrete? & Contributions \\

@@

\multirow{1}{.55\textwidth}{{\bf Finance:} Portfolio selection optimization} && \multirow{1}{.25\textwidth}{\cite{deng-etal:2013,kallrath:2003,lin-etal:2005,maranas-etal:1997,parpas-rustem:2006,rios-sahinidis:2010}} \\ 

@@

@@

>>>>

@@

On the other hand, (MI)QP is, in some sense, a considerably more expressive class than (MI)LP. Quadratic expressions are found, either naturally or after appropriate reformulations, in very many optimization problems \cite{Kochenberger2014}. Table \ref{tbl:application} provides a certainly non-exhaustive collection of applications that lead to formulations with either quadratic constraints, ot quadratic objective function, or both. Also, in general any continuous function can be approximated with arbitrary accuracy (over a compact set) by a polynomial of arbitrary degree; in turn, every polynomial can be broken down to a system of quadratic expressions. Hence, (MI)QP is, in some sense, roughly as expressive as the whole of (MI)NLP. Of course this is, in principle, true for (MI)LP as well, but at the cost of much larger and much more complex formulations ({\bf citations?}). Hence, for many applications QP may represent the ``sweet spot'' between the effectiveness, but lower expressive power, of (MI)LP and the higher expressive power, but much higher computational cost, of (MI)NLP.

@@

Problem & Discrete & Contributions \\

@@

\multirow{1}{.55\textwidth}{{\bf Finance:} Portfolio optimization} & checkmark & \multirow{1}{.25\textwidth}{\cite{deng-etal:2013,kallrath:2003,lin-etal:2005,maranas-etal:1997,parpas-rustem:2006,rios-sahinidis:2010,FrFG16,FrGe06a,FrGe07a,FrGe09a}} \\ 

@@

\multirow{1}{.55\textwidth}{Quadratic network design} & \checkmark & \cite{FrFG16,FGGP11} \\ \cmidrule(rl){2-3}

@@

\multicolumn{3}{l}{{\bf Telecommunications}} \\[1pt]
\multirow{1}{.55\textwidth}{Delay-constrained routing} & \checkmark & \cite{FrGaSc14,FrGaSt16a} \\
\multicolumn{3}{l}{{\bf Energy}} \\[1pt]
\multirow{1}{.55\textwidth}{Unit-commitment problem} & \checkmark & \cite{Tetal15} \\
